A* with Perfect Potentials

### 2020-05-05 paper/ch_potentials.tex
subsection -> section
start with experimental eval section

\usepackage{wrapfig}
\usepackage[algo2e,vlined]{algorithm2e}

@@

\subsection{Avoid Dead-Ends using Largest Biconnected Component}

@@

\begin{itemize}
\item Avoid nothing running times, i.e., what is if $w_q = w_\ell$?
\item Multiply all weights by $\alpha$, i.e., $w_q = \alpha w_\ell$ for $\alpha$ in 1.1, 1.5, 2, 3
\item Avoid highway
\item Avoid tunnel
\item Avoid highway + tunnel
\item MapBox Live Traffic
\item Ptv-TD traffic? Achtung: Das Fass würde ich nicht aufmachen. Am Ende will ein Reviewer, dass wir avoid highway mit TD kombinieren... das ist NP-schwer
\item Running times if OSM degree 2 nodes are not extracted! Das einzige Argument pro Erhalten von Deg 2 das ich bisher kenne ist MapBox Live Traffic matchen.
\end{itemize}

@@

\begin{itemize}
\item Effectiveness of A*
	\begin{itemize}
  \item Multiplied weights by 1 to 2 in steps of 0.05
  \item On DIMACs Eur
  \item Plot x factor, y running time
  \end{itemize}

\item Algo Building Blocks
	\begin{itemize}
  \item DIMACs Eur x1.1
  \item Table
  	\begin{itemize}
    \item columns: running time, potential evals, relaxed arcs
    \item rows: (Dijkstra, SCC, Deg2, Deg3) x (CH Pot or not)
    \item or transposed?
		\end{itemize}
	\end{itemize}

\item Applications
	\begin{itemize}
  \item Table
  	\begin{itemize}
    \item columns: preprocessing time, running time, potential evals, relaxed arcs, shortest path distance / lower bound, dijkstra running time?
    \item rows: OSM Ger Mapbox Live, forbidden highways, forbidden tunnels, TD Ger06, TD Eur17, DIMACs Eur 1000 {Random|Fastest} Arcs {x2, x10}
		\end{itemize}
	\end{itemize}
\end{itemize}

>>>>

\usepackage{wrapfig}
\usepackage{booktabs}
\usepackage[algo2e,vlined]{algorithm2e}

@@

\section{Avoid Dead-Ends using Largest Biconnected Component}

@@

\label{sec:experiments}

In this section, we present our experimental evaluation.
Our benchmark machine runs openSUSE Leap 15.1 (kernel 4.12.14), and has 128\,GiB of DDR4-2133 RAM and an Intel Xeon E5-1630 v3 CPUs which has four cores clocked at 3.7\,Ghz and 4~$\times$~32\,KiB of L1, 8~$\times$~256\,KiB of L2, and 10\,MiB of shared L3 cache.
All experiments were performed sequentially.
Our code is written in Rust and compiled with rustc 1.44.0-nightly in the release profile with the target-cpu=native option.

\subparagraph{Inputs and Methodology}
We perform experiments on several graphs with travel time weights which we modify in different ways.
Preprocessing running times are averages over 10 runs.
For the queries, we perform 10\,000 point-to-point queries where both source and target are nodes drawn uniformly at random and report average results.
Our main benchmark instance is a graph of the road network of Western Europe made publicly available for the Ninth DIMACS implementation Challenge~\cite{DemetrescuGJ09} with 18M nodes and 42M edges.
Additionally, we perform experiments on a recent OSM instance of Germany\footnote{\url{https://download.geofabrik.de/europe/germany.html}, obtained on August 2nd, 2019}.
To obtain the routing graph, we use the import from RoutingKit\footnote{\url{https://github.com/RoutingKit/RoutingKit}}.
The graph has 11M nodes and 26M edges.
For this instance, we have proprietary live traffic snapshot from Friday 2019/08/02 afternoon provided by Mapbox\footnote{\url{https://www.mapbox.com/}}.
The live data comes in the form of 320K OSM node pairs and live speeds for the link between the nodes.
We also have two graphs with traffic predictions provided by PTV\footnote{\url{https://ptvgroup.com}}.
One is an old instance of Germany from 2006 (4.7M nodes, 10.7M edges) and the other a newer instance of Europe (25.8M nodes, 55.5M edges).

\begin{figure}
\centering
\includegraphics[width=\textwidth]{fig/scaled_weights.pdf}
\caption{Query running times for queries of DIMACs Europe with scaled edge weights.}\label{fig:scaled_weights}
\end{figure}

\begin{table}
\centering
\caption{Query performance with the different algorithmic features.}\label{tab:building_blocks}
\begin{tabular}{lrrr}
\toprule
{} & Running Time &     Queue Pops &   Relaxed Arcs \\
{} &         [ms] & [$\cdot 10^3$] & [$\cdot 10^6$] \\
\midrule
No Deg2, No Deg3, No SCC, No Pot. & 1765 & 7087.0 & 19.6 \\
No Deg2, No Deg3, No Pot.         & 1308 & 6249.8 & 17.3 \\
No Deg3, No Pot.                  & 1180 & 5233.7 & 16.5 \\
No Pot.                           &  901 & 3035.5 & 15.1 \\
No Deg2, No Deg3, No SCC          &  547 & 1006.4 &  2.7 \\
No Deg2, No Deg3                  &  469 &  905.2 &  2.5 \\
No Deg3                           &  410 &  767.5 &  2.4 \\
                                  &  315 &  445.0 &  2.2 \\
\bottomrule
\end{tabular}
\end{table}

@@

\begin{itemize}
\item Applications
	\begin{itemize}
  \item Table
  	\begin{itemize}
    \item columns: preprocessing time, running time, potential evals, relaxed arcs, shortest path distance / lower bound, dijkstra running time?
    \item rows: OSM Ger Mapbox Live, forbidden highways, forbidden tunnels, TD Ger06, TD Eur17, DIMACs Eur 1000 {Random|Fastest} Arcs {x2, x10}
		\end{itemize}
	\end{itemize}
\end{itemize}
